The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2014-01-14 document/ms.tex
updating code and document to use 'slow-roll' condition
'outline' of method section

@@

The basic idea is that we have some function $f(t)$ that returns the
instantaneous flux of the system at time $t$ but we would like to compute the
integrated flux over an exposure time \texp
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
    \quad.
\end{eqnarray}
Following Kipping, this can be approximated as
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &\approx&
    \frac{f(t_0-\texp/3)+f(t_0)+f(t_0+\texp/3)}{3} \quad.
\end{eqnarray}
We extend this by recursively defining this approximation as
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &\approx&
    \frac{f_\mathrm{int}(t_0-\texp/3;\texp/3)+f_\mathrm{int}(t_0;\texp/3)
          +f_\mathrm{int}(t_0+\texp/3;\texp/3)}{3}
\end{eqnarray}
where the recursive depth is set by a tolerance on
\begin{eqnarray}
\left | f(t_0-\texp/3)-2\,f(t_0)+f(t_0+\texp/3) \right | &\le& \epsilon
\end{eqnarray}
where $\epsilon$ is a free parameter quantifying the required accuracy of the
method.

>>>>

\section{Sampling method}

We sampled the posterior probability in equation SOMEEQN using the affine
invariant ensemble sampler (CITE: GW, emcee).
This method is perfect for this project because it tends to require very
little tuning even when applied to new datasets.

\paragraph{Ensemble specifications}
We run with 48 walkers on 24 cores on the BuTinah cluster at NYUAD.

\paragraph{Initialization}
We start sampling in a \emph{tiny} isotropic Gaussian ball (HOW BIG) centered
at the parameters given in the KOI catalog.
Then, we run 2000 iterations of MCMC and re-sample the walkers in a similarly
time Gaussian ball around the maximum probability point seen in that run.

\paragraph{Production chain}
Finally we run the production chain---re-estimating the integrated
auto-correlation time for each parameter---until we have at least $128 \times
N_\mathrm{walkers}$ independent samples for ever parameter.

\paragraph{Analysis of convergence}

\section{Results}

@@

The basic idea is that we have some function $f(t)$ that returns the
instantaneous flux of the system at time $t$ but we would like to compute the
integrated flux over an exposure time \texp
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &=& \int_{t_0-\texp/2}^{t_0+\texp/2} f(t) \dd t
    \quad.
\end{eqnarray}
Following Kipping, this can be approximated as
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &\approx&
    \frac{f(t_0-\texp/3)+f(t_0)+f(t_0+\texp/3)}{3} \quad.
\end{eqnarray}
We extend this by recursively defining this approximation as
\begin{eqnarray}
f_\mathrm{int}(t_0;\texp) &\approx&
    \frac{f_\mathrm{int}(t_0-\texp/3;\texp/3)+f_\mathrm{int}(t_0;\texp/3)
          +f_\mathrm{int}(t_0+\texp/3;\texp/3)}{3}
\end{eqnarray}
where the recursive depth is set by a tolerance on
\begin{eqnarray}
\left | \frac{f(t_0-\texp/3)-2\,f(t_0)+f(t_0+\texp/3)}
             {f(t_0-\texp/3)-f(t_0+\texp/3)} \right | &\le& \epsilon
\end{eqnarray}
where $\epsilon$ is a free parameter quantifying the required accuracy of the
method.
